MyStoryKnight: A Character-drawing Driven Storytelling System Using LLM Hallucinations

### 2023-12-22 paper_interaction_conf/main.tex
Add new references and update system architecture and user interface

\usepackage{graphicx}
\usepackage{latexsym}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/1920x720px.png}
    \caption{MyStoryKnight system overview.}
    \label{fig:system-overview}
\end{figure*}

@@

%3
\section{System Overview}

%4
\section{Implementation}

%5
\section{Evaluation}

%6
\section{Discussion}

%7
\section{Conclusion}

>>>>

\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{url}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/2400x600px.png}
    \caption{MyStoryKnight system overview.}
    \label{fig:system-overview}
\end{figure*}

@@

%3
\section{System Overview}
\label{sec:system-overview}
To address these issues, we designed \textbf{MyStoryKnight}, an interactive storytelling that uses drawings as input and utilizes LLM hallucinations to generate a branching story. Agency is a critical factor in interactive storytelling \cite{11:LimaGV20}, as it promotes engagement and immersion \cite{12:ZhangXWYRWYWL22}. Our system supports user agency by allowing users to navigate the story through their choices. Additionally, we use a complexity analysis algorithm to guide the LLM hallucinations to generate a coherent and consistent story, fitting for children's comprehension.

\subsection{System Architecture}
\label{subsec:system-architecture}
The system architecture is shown in Figure \ref{fig:system-architecture}. The system consists of three main components:
\begin{enumerate}
    \item \textbf{Drawing Analysis}: Extracting visual features from the user's drawing. The visual features are used as a prompt for the LLM to hallucinate a character description and a background story.
    \item \textbf{Story Generator}: Story is generated based on user selection on a set of actions. LLM hallucinations are used to generate the story and actions.
    \item \textbf{Complexity Analysis}: Natural language processing (NLP) techniques are used to analyze the story's coherency and consistency. The results are used to guide the LLM hallucinations.
\end{enumerate}
To achieve out goals, we utilize GPT-4 \cite{17:abs-2303-08774} for drawing analysis and story generation. Additionally, we use spacy \cite{18:spacy} in addition to GPT-4 for complexity analysis. The system is implemented with Django, a Python web framework \cite{19:django}, and React, a JavaScript library for building user interfaces \cite{20:react}.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/800x600px.png}
    \caption{System architecture.}
    \label{fig:system-architecture}
\end{figure}

\section{User Interface}
\label{sec:user-interface}
The user interface is shown in Figure \ref{fig:user-interface}. There are three

\begin{figure}[t]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/800x600px.png}
    \caption{User interface.}
    \label{fig:user-interface}
\end{figure}

\subsection{Interaction Flow}
\label{subsec:interaction-flow}

%4
\section{Conclusion}
